### 2023-10-29 generalExploration.Rmd
move summary out of agent loop

pos=random2Dgrid(K=K,Gx=100)
initcomus=initialiseCommunities(traits=a,coordinates=pos)
size=table(sapply(population,"[[","community"))
initcomus$size=size
plot(initcomus$coordinates,pch=21,bg=apply(initcomus$adaptivetraits,1,mean)+1,cex=log(initcomus$size))

tstep=1000
popsize=c()
popsum=list()
for(time in 1:tstep){
    if(logging=="time")print(paste("------",time,"------"))
    for(i in sample(1:length(population))){
        ind=tryCatch(population[[i]]$id,error=function(e)NULL)
        if(!is.null(ind)){
            ##ageing

@@

        #quickly summarize
        popsum[[time]]=sapply(names(population[[1]]),function(n)table(sapply(population,"[[",n)))
        ##
        plot(initcomus$coordinates,pch=21,bg=apply(initcomus$adaptivetraits,1,mean)+1,cex=log(initcomus$size))
        popsize=c(popsize,length(population))
    }

@@

>>>>

pos=random2Dgrid(K=K,Gx=100)
initcomus=initialiseCommunities(traits=a,coordinates=pos)
size=table(sapply(population,"[[","community"))
initcomus$size=size
plot(initcomus$coordinates,pch=21,bg=apply(initcomus$adaptivetraits,1,mean)+1,cex=log(initcomus$size))
logging="time"
tstep=1000
popsize=c()
popsum=list()
for(time in 1:tstep){
    if(logging=="time")print(paste("------",time,"------"))
    for(i in sample(1:length(population))){
        ind=tryCatch(population[[i]]$id,error=function(e)NULL)
        if(!is.null(ind)){
            ##ageing

@@

@@

    #quick summary of population at time 
    popsum[[time]]=sapply(names(population[[1]]),function(n)table(sapply(population,"[[",n)))

    ##
    plot(initcomus$coordinates,pch=21,bg=apply(initcomus$adaptivetraits,1,mean)+1,cex=log(initcomus$size))
    popsize=c(popsize,length(population))
